\section{Algorithm Implementation}

\subsection{Essential Network Metrics Calculation}

To gain insights into the structure and properties of the network, essential network metrics need to be calculated. These metrics include measures like betweenness centrality, PageRank, clustering coefficient, degree centrality, and average neighbor degree. These calculations provide information about the importance, influence, connectivity, and overall structure of nodes within the network.

\subsection{Identifying Key Nodes and Communities}

Identifying key nodes and communities within the network is an important step in understanding its structure and dynamics. This involves techniques such as community detection algorithms, which aim to identify groups of nodes that are more densely connected internally than with the rest of the network. Key nodes can be identified based on their centrality measures, such as betweenness centrality or PageRank, which indicate their importance in the network.

\subsection{Evaluating Network Centrality}

Network centrality measures the importance or influence of individual nodes within the network. It provides insights into the most influential or central nodes, which play a crucial role in the overall network structure. Evaluating network centrality involves analyzing metrics like degree centrality, betweenness centrality, and closeness centrality. By understanding the centrality of nodes, it becomes possible to identify key players, opinion leaders, or influential entities within the network.